\vspace{50pt}\\ \huge \bfseries SKEDGE \\ \vspace{10pt} \Large Smarter course scheduling for our\\ University of Rochester

### 2016-04-11 paper.tex
work on social... so slow
More splitup
Small fixes

\title{
\vspace{60pt}\\
\huge \bfseries SKEDGE
\\
\vspace{10pt}
\Large
Smarter course scheduling for our\\
University of Rochester
}

@@

\date{April 12, 2016\\
    \vspace{150pt}\\
    submitted in partial fulfillment of\\
    the requirements for the degree\\
    \emph{honors bachelor of science}\\
}

@@

In this paper I present Skedge, a web application for students to comfortably and effectively engage with the University's course catalog. Skedge matches and surpasses the capabilities of the existing University tool for this purpose, ``Course Description / Course Schedule'' (CDCS) and presents its information in a more visually pleasing way. As a result, Skedge boasts strong user-retention rates, long session durations, and high student adoption despite having virtually no advertisement. Through collected usage data, I demonstrate that a) Skedge's differences from and additions to CDCS are usable and have real need, b) the two major use-cases associated with course browsing---direct search and exploratory search---are effectively accommodated by Skedge, and c) Skedge's search mechanism is user-friendly and self-teaches to users over time.

@@

\include{future}
\clearpage

@@

	\bibitem{kpcb} Takis Konstantopoulos {\em Introductory lecture notes on
		Markov Chains and Random Walks.} Uppsala University,
		\\\url{http://www2.math.uu.se/~takis/L/McRw/mcrw.pdf}

>>>>

\title{
\vspace{50pt}\\
\huge \bfseries SKEDGE
\\
\vspace{10pt}
\Large
Smarter course scheduling for our\\
University of Rochester
}

@@

\date{April 12, 2016\\
    \vspace{100pt}\\
    submitted in partial fulfillment of\\
    the requirements for the degree\\
    \emph{honors bachelor of science}\\
    \vspace{30pt}\\
    and as an open letter addressed to\\
    the information technology staff\\
    at the university of rochester
    \vspace{-30pt}
}

@@

In this paper I present Skedge, a web application for students to comfortably and effectively engage with the University's course catalog. Skedge matches and surpasses the capabilities of the existing University tool for this purpose, ``Course Description / Course Schedule'' (CDCS) and presents its information in a more visually appealing way. As a result, Skedge boasts strong user-retention rates, long session durations, and high student adoption despite having virtually no advertisement. Through collected usage data, I demonstrate that \textbf{a)} Skedge's differences from and additions to CDCS are usable and have real-world need, \textbf{b)} the three major use-cases associated with course browsing---direct search, exploratory search, and peer recommendation---are effectively accommodated by Skedge, and \textbf{c)} Skedge's novel search mechanism is user-friendly and self-teaches to users over time.

@@

@@

	\bibitem{kpcb} Meeker, Mary (2015). http://www.slideshare.net/kleinerperkins/internet-trends-v1
